Thermodynamic fragments for magic states in quantum computation

### 2021-04-12 magic_paper.tex
Cleaned up Sec.V. What to do with last elbow? How to clean up lower bounds subsection?

We now generalise the approach taken in the previous section and consider bounds on magic distillation for an arbitrary stabiliser fragment, $\R_\sigma$ where $\sigma$ is any quantum state $\sigma \in \stab$.
In other words, we consider those bounds on distillation that apply when the free operations have $\sigma$ as a fixed point.

These bounds can be interpreted in two different ways: 
\begin{enumerate}
\item As family of upper bounds parameterized by an abstract stabiliser state $\sigma$.
\item The state $\sigma$ corresponds to actual hardware limitations or to biased noise model in which $\sigma$ is an equilibrium state of some kind. 
\end{enumerate}
Without loss of generality, we can always write a full-rank stabiliser state $\sigma$ in the form $\sigma =  \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and effective Hamiltonian $H$. Our results will also depend on the free energy $F(\beta)$ of the state $\sigma$, which is defined by
\begin{equation}
	F(\beta) \coloneqq \tr[H \sigma] - \beta^{-1}S(\sigma) = -\beta^{-1}\log{\Z_\beta}.
\end{equation}
Here $S(\sigma)$ is the von Neumann entropy $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$. Again, under interpretation (1) above this is an abstract entropic measure of the stabilizer state, while under interpretation (2) it corresponds to the thermodynamic free energy of the equilibrium state.

We focus on the distillation process
\begin{equation}\label{eq:stdist}
	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \sigma^{\otimes (n-n')},
\end{equation}
and as before tensoring in copies of $\sigma$ does not affect the Lorenz curves of the magic states in the fragment.

@@

\begin{theorem}\label{thm:stab_bounds}
	Given any theory of magic $\R = (\F, \O)$. Let $\sigma$ be any qutrit stabiliser state, and write the state as $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0, E_1, E_2$, and where $\beta$ is an effective inverse temperature for the state. 
We define $\beta_\star = (1/kT_\star)$ through the relation
\begin{equation}
	E_{\rm max} - E_s =: kT_\star \ln 2,
\end{equation}
where $E_{\rm max} = \max\{E_k\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$.  For $\beta \leq \beta_\star$ define a threshold noise level
\begin{equation}
	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm max} - E_s)\beta}}.
\end{equation}
Then any distillation rate $R(\epsilon, \beta)$ in the $\sigma$--fragment of a magic theory is bounded as follows:\\
If $\beta \leq \beta_{\star}$ and $\epsilon  \leq \epsilon_{\star}$,
\begin{equation}
	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_s - F(\beta))}.
\end{equation}
If $\beta \leq \beta_{\star}$ and $\epsilon_{\star} < \epsilon$, then
\begin{equation}
	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_{\rm max} - E_s)(\beta_{\star} - \beta)}{\beta (E_s - F(\beta))}.
\end{equation}
Otherwise if $\beta > \beta_{\star}$,
\begin{equation}
	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_{\rm max} - F(\beta))}.
\end{equation}
In the above expressions $F(\beta)$ is the effective free energy of the stabilizer state.
\end{theorem}
A few comments can be given on this result. 
Firstly, the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
Secondly, these bounds are derived based on analysis of only a part of the Lorenz curves and can be improved via a finer analysis. 
This is apparent by simple numerical calculations on the entirety of the curves.
Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure. 
Finally, it is notable that we obtain a Landauer-like condition with a characteristic temperature $kT_\star \ln 2 = E_{\rm max} - E_s$, where $kT_\star = \beta_\star^{-1}$. 
It is unclear whether this points to a generic feature that can be directly related to fundamental thermodynamic relations, such as the erasure cost of a single bit being $kT \ln 2$. 
Given that we work with qutrits this seems surprising, but does deserve further study.

@@

Let $\displaystyle \sigma = e^{-\beta H} / \Z_\beta$ be a stabiliser state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$, where we have $E_0 \le E_1 \le E_2$.
The stabilizer state $\sigma$ can now be written as 
\begin{equation}
	\sigma = \frac{e^{-\beta E_0}}{\Z_\beta} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z_\beta} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z_\beta} \ketbra{\varphi_2},
\end{equation}
where $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis. Let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$. Since the Clifford group is the normalizer of the Heisenberg-Weyl group this implies that $C$ is a Clifford unitary. Therefore, $C$ maps $\sigma$ to another stabilizer state that is diagonal in the computational basis, and we can therefore assume without loss of generality that $\sigma$ is diagonal in $\{|0\>,|1\>, |2\>\}$. However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the strange state will be transformed on the discrete phase space. We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.

The Wigner distribution of state $\sigma$ is then given by
\begin{align}
	\W[\bmx]{\sigma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}W_{\ketbra{k}}(x_0,x_1) \nonumber\\
	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x_0, k} = \frac{e^{-\beta E_{x_0}}}{3\Z_\beta},
\end{align}
where $x_0$ is the first component of $\x$, labeling one of the three vertical lines in the phase space.
Since we have restricted to full-rank states, all Wigner components are strictly positive, and so the pre-order $\prec_{\sigma}$ is well-defined. States that are not full-rank can be addressed as a limiting case of the above.

@@

Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho^{\otimes n}_S |\sigma^{\otimes n})$ are computed in~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}. The values are denoted by $w_{ijk}$ and with associated multiplicity $m_{ijk}$. The indices $i,j,k$ obey the constraint $\alpha \coloneqq i+j+k \leq n$.
The $n$--copy multiplicity is given by
\begin{equation}
	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k,
\end{equation}
while the distribution values are given by
\begin{align}
	w(\rho_{\rm{S}} | \sigma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )}.
\end{align}

In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\sigma}$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \sigma)_{ijk}$ in decreasing order.
In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum component,
\begin{align}
	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{max}} \coloneqq (3\Z)^{n}\times \nonumber\\
	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
\end{align}
where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
We can also assume that $n$ is even, so that we need the sum $\alpha = i+j+k$ to be even for the expression to be positive.

Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
\end{align}
If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$. 
To determine this transition we set
\begin{equation}\label{eq:noise_transition}
	\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)} \coloneqq \frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_s)} = 1.
\end{equation}
We want to find in which cases there exists a threshold noise level $\epsilon_\star$ at which the transition in~\cref{eq:noise_transition} occurs.
If $E_{\rm{max}} = E_0$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$. 
Otherwise, there is a threshold temperature value $\beta_\star$ given by
\begin{equation}
	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2.
\end{equation}
Below the threshold, $0 \leq \beta \leq \beta_\star$, the transition is well defined and the threshold noise level at which it occurs is given by
\begin{equation}
	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_s)\beta}}.
\end{equation}
This encompasses the case $E_{\rm{max}} = E_0$.
For $\beta > \beta_\star$, we have
\begin{equation*}
	\frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_s)} > \frac{3-\epsilon}{6-8\epsilon} 2 \geq \frac{1}{2}2 = 1,
\end{equation*}
so there is no transition and we set $\epsilon_\star = 0$.

The maximum component can then be expressed as
\begin{equation}
\bmw(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
	\begin{cases}
		(3\Z)^{n} v^n e^{n\beta E_s}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
Case $\rm{(C2)}$ corresponds to
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
	\end{cases}
\end{equation}
and we have $E_{\rm{max}} \ne E_s$, so the multiplicity in each case is $3^n$.

The coordinates of the first elbow are now given by
\begin{equation}\label{eq:first_elb_coords}
	(x_0, L_0) =
	\begin{cases}
		\left(\frac{1}{3^n} e^{-n\beta (E_s - F(\beta))}, v^n \right), &\rm{(C1)}	\vspace{10pt}\\
		\left( e^{-n\beta (E_{\rm{max}}-F(\beta))}, (3u)^n \right). &\rm{(C2)} 
	\end{cases}
\end{equation}
The Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$, depending on the physical parameters $\epsilon, \epsilon', \beta$.
Specifically, we have three scenarios of relevance to magic distillation:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_s$ or $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $E_{\rm{max}} > E_s$, $\beta \geq \beta_{\star}$.
\end{enumerate}
The fourth case $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon' > \epsilon$ \ddd{[True?]}, which means that the output magic state is noisier than the input state.

In each of the three scenarios, it is simple to check that the initial state's first elbow has $x_0$ coordinate closer to $0$) than that of the output state: $x_0 \leq x_0'$, see~\cref{app:first_elb_loc} for details. Therefore we obtain distillation bounds directly by comparing $L_0$ and $L_0'$.  We we do so we obtain the following distillation bounds,
\begin{equation}\label{eq:rate_bounds_proof}
	R \leq
	\begin{cases}
		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
	\end{cases}
\end{equation}
Substituting $\epsilon' = 0$ into these expressions leads to the stated distillation bounds.

>>>>

We now generalise the approach taken in the previous section and consider bounds on magic distillation for an arbitrary stabiliser fragment $\R_\sigma$, where $\sigma$ is any quantum state $\sigma \in \stab$.
In other words, we consider those bounds on distillation that apply when the free operations have $\sigma$ as a fixed point.

These bounds can be interpreted in two different ways: 
\begin{enumerate}
\item As a family of upper bounds parameterised by an abstract stabiliser state $\sigma$.
\item The state $\sigma$ can also reflect actual hardware limitations or some kind of biased noise model in which $\sigma$ is an equilibrium state.
\end{enumerate}
Without loss of generality, we can always write a full-rank stabiliser state $\sigma$ in the form $\sigma =  \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and effective Hamiltonian $H$. Our results will also depend on the free energy $F(\beta)$ of the state $\sigma$, expressed as
\begin{equation}
	F(\beta) \coloneqq \tr[H \sigma] - \beta^{-1}S(\sigma) = -\beta^{-1}\log{\Z_\beta}.
\end{equation}
Here $S(\sigma)$ is the von Neumann entropy $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$. Again, under interpretation (1) above, this is an abstract entropic measure of the stabilizer state, while, under interpretation (2), it corresponds to the thermodynamic free energy of the equilibrium state.

We focus on the distillation process
\begin{equation}\label{eq:stdist}
	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \sigma^{\otimes (n-n')},
\end{equation}
where, as before, tensoring in copies of $\sigma$ does not affect the Lorenz curves of the magic states in the fragment.

@@

\begin{theorem}\label{thm:stab_bounds}
	Given a theory of magic $\R = (\F, \O)$, let $\sigma$ be any qutrit stabiliser state, and write the state as $\sigma = \frac{1}{\Z} e^{-\beta H}$, where $H$ has eigenvalues $E_0, E_1, E_2$, and $\beta$ is an effective inverse temperature for the state. 
We define $\beta_\star = 1/kT_\star$ through the relation
\begin{equation}
	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
\end{equation}
where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$. \nick{is the ``overlap'' statement precise enough?} For $\beta \leq \beta_\star$, we define a threshold noise level
\begin{equation}
	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm max} - E_s)\beta}}.
\end{equation}
Then, any distillation rate $R(\epsilon, \beta)$ in the $\sigma$--fragment of a magic theory is bounded as follows:\\
If $\beta \leq \beta_{\star}$ and $\epsilon  \leq \epsilon_{\star}$,
\begin{equation}
	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_s - F(\beta))}.
\end{equation}
If $\beta \leq \beta_{\star}$ and $\epsilon_{\star} < \epsilon$, then
\begin{equation}
	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_{\rm max} - E_s)(\beta_{\star} - \beta)}{\beta (E_s - F(\beta))}.
\end{equation}
Otherwise if $\beta > \beta_{\star}$,
\begin{equation}
	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_{\rm max} - F(\beta))}.
\end{equation}
In the above expressions $F(\beta)$ is the effective free energy of the stabilizer state.
\end{theorem}
A few comments can be given on this result. 
Firstly, the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
Secondly, these bounds are derived based on analysis of only a part of the Lorenz curves and can be improved via a finer analysis. 
This is apparent by simple numerical calculations on the entirety of the curves.
Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure. 
Finally, it is notable that we obtain a Landauer-like condition with a characteristic temperature $kT_\star \ln 2 = E_{\rm max} - E_s$, where $kT_\star = \beta_\star^{-1}$. 
It is unclear whether this points to a generic feature that can be directly related to fundamental thermodynamic relations, such as the erasure cost of a single bit being $kT \ln 2$. 
Given that we work with qutrits this seems surprising, but does deserve further study.

@@

Let $\displaystyle \sigma = e^{-\beta H} / \Z_\beta$ be a stabiliser state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$.
The stabilizer state $\sigma$ can now be written as 
\begin{equation}
	\sigma = \frac{e^{-\beta E_0}}{\Z_\beta} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z_\beta} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z_\beta} \ketbra{\varphi_2},
\end{equation}
where $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis. Let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$. Since the Clifford group is the normalizer of the Heisenberg-Weyl group this implies that $C$ is a Clifford unitary. Therefore, $C$ maps $\sigma$ to another stabilizer state that is diagonal in the computational basis, and we can therefore assume without loss of generality that $\sigma$ is diagonal in $\{|0\>,|1\>, |2\>\}$. However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the strange state will be transformed on the discrete phase space. We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.

The Wigner distribution of state $\sigma$ is then given by
\begin{align}
	\W[\bmx]{\sigma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}W_{\ketbra{k}}(x, p) \nonumber\\
	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x, k} = \frac{e^{-\beta E_{x}}}{3\Z_\beta},
\end{align}
where $x$ labels one of the three vertical lines in the phase space.
Since we have restricted to full-rank states, all Wigner components are strictly positive, and so the pre-order $\prec_{\sigma}$ is well-defined. States that are not full-rank can be addressed as a limiting case of the above.

@@

Using this notation, the values and multiplicities of the $n$--copy distribution $\bmw(\rho^{\otimes n}_S |\sigma^{\otimes n})$ are computed in~\cref{lem:ncopycomponents} in~\cref{app:cmpairs}. The values are denoted by $w(\rho_{\rm{S}} | \sigma)_{ijk}$ with associated multiplicity $m_{ijk}$. The indices $i,j,k$ are non-negative integers and obey the constraint $\alpha \coloneqq i+j+k \leq n$.
The $n$--copy multiplicity is given by
\begin{equation}
	m_{ijk} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k,
\end{equation}
while the distribution values are given by
\begin{align}\label{eq:ncopy_w_rescaled}
	w(\rho_{\rm{S}} | \sigma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )},
\end{align}
where we have also computed the unscaled components
\begin{align}
	w(\rho_{\rm{S}})_{ijk} &= (-v)^{n-\alpha} u^{\alpha}, \label{eq:ncopy_wrho}\\
	w(\sigma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_s} e^{-\beta ( i E_0 + j E_1 + k E_2 )}. \label{eq:ncopy_wsigma}
\end{align}

In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\sigma}$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \sigma)_{ijk}$ in decreasing order.
In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum component,
\begin{align}
	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} \coloneqq (3\Z)^{n}\times \nonumber\\
	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
\end{align}
where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
We can also assume that $n$ is even, so that we need the sum $\alpha = i+j+k$ to be even for the expression to be positive.

Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
\end{align}
If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$. 
To determine this transition we set
\begin{equation}\label{eq:noise_transition}
	\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)} \coloneqq \frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_s)} = 1.
\end{equation}
We want to find in which cases there exists a threshold noise level $\epsilon_\star$ at which the transition in~\cref{eq:noise_transition} occurs.
If $E_{\rm{max}} = E_0$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$. 
Otherwise, there is a threshold temperature value $\beta_\star$ given by
\begin{equation}
	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2.
\end{equation}
Below the threshold, $0 \leq \beta \leq \beta_\star$, the transition is well defined and the threshold noise level at which it occurs is given by
\begin{equation}
	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_s)\beta}}.
\end{equation}
This encompasses the case $E_{\rm{max}} = E_0$.
For $\beta > \beta_\star$, we have
\begin{equation*}
	\frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_s)} > \frac{3-\epsilon}{6-8\epsilon} 2 \geq \frac{1}{2}2 = 1,
\end{equation*}
so there is no transition and we set $\epsilon_\star = 0$.

The maximum component can then be expressed as
\begin{equation}
w(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
	\begin{cases}
		(3\Z)^{n} v^n e^{n\beta E_s}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
Case $\rm{(C2)}$ corresponds to
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
	\end{cases}
\end{equation}
so the multiplicity in each case is $3^n$.

Using the appropriate indices in~\cref{eq:ncopy_wrho,eq:ncopy_wsigma}, the first elbow coordinates can now be expressed as
\begin{equation}\label{eq:first_elb_coords}
	(x_0, L_0) =
	\begin{cases}
		\left(\frac{1}{3^n} e^{-n\beta (E_s - F(\beta))}, v^n \right), &\rm{(C1)}	\vspace{10pt}\\
		\left( e^{-n\beta (E_{\rm{max}}-F(\beta))}, (3u)^n \right). &\rm{(C2)} 
	\end{cases}
\end{equation}
The Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$, depending on the physical parameters $\epsilon, \epsilon', \beta$.
Specifically, we have three scenarios of relevance to magic distillation:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_s$ or $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $E_{\rm{max}} > E_s$, $\beta \geq \beta_{\star}$.
\end{enumerate}
The fourth case $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon$, which would imply that the output magic state is noisier than the input state.

In each of the three scenarios, it is simple to check that the initial state's first elbow has $x_0$ coordinate closer to $0$ compared to the output state, $x_0 \leq x_0'$ (see~\cref{app:first_elb_loc} for details). Therefore, we can use the first elbow constraint, as described in~\cref{app:elb_constraints}, leading to the following distillation bounds,
\begin{equation}\label{eq:rate_bounds_proof}
	R \leq
	\begin{cases}
		\dfrac{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_s - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_s - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
		\dfrac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F(\beta))}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)}.
	\end{cases}
\end{equation}
Substituting $\epsilon' = 0$ into these expressions leads to the stated distillation bounds.
